Pitfall of Prediction-orienterd Machine Learning Methods and Economic Value of Statistical Efficiency in On-farm Precision Experimentation

### 2022-02-26 Writing/appendix.rmd
code for tables modified

# Pairwise t-test of yield RMSE, EONR RMSE, and profit between models {-}
```{r count-table, echo=FALSE, cache=FALSE}

prt_table <-
  est_data %>%
  .[order(sim, model), ] %>%
  .[, y := (rmse_cv == min(rmse_cv)), by = .(sim, field_size)] %>%
  .[, eonr := (rmse_eonr == min(rmse_eonr)), by = .(sim, field_size)] %>%
  .[, profit := (profit == max(profit)), by = .(sim, field_size)] %>%
  .[,
    .(
      yield = (mean(y) * 100) %>% round(2),
      EONR = (mean(eonr) * 100) %>% round(2),
      profit = (mean(profit) * 100) %>% round(2)
    ),
    by = .(field_size, model)
  ]

#* create a table
count_table <-
  prt_table %>%
  # === Wide to Long: melt()
  melt(id.vars = c("field_size", "model")) %>%
  # === Long to Wide: dcast()
  dcast(field_size + variable ~ model, value.var = "value")

#* displary the table
knitr::kable(count_table,
  format = "markdown",
  caption = "Percentage (%) of each model being the best-performing among the five models in a single simulation round"
)
```

>>>>

# Pairwise t-test of yield RMSE, EONR RMSE, and profit between models {-}
```{r count-table, tab.cap = "Percentage (%) each model performs the best for yield prediction, EONR prediction, and profit", echo=FALSE, cache=FALSE}

prt_table <-
  est_data %>%
  .[order(sim, model), ] %>%
  .[, y := (rmse_cv == min(rmse_cv)), by = .(sim, field_size)] %>%
  .[, eonr := (rmse_eonr == min(rmse_eonr)), by = .(sim, field_size)] %>%
  .[, profit := (profit == max(profit)), by = .(sim, field_size)] %>%
  .[,
    .(
      yield = (mean(y) * 100) %>% round(2),
      EONR = (mean(eonr) * 100) %>% round(2),
      profit = (mean(profit) * 100) %>% round(2)
    ),
    by = .(field_size, field_col, model)
  ]

#* create a table
count_table <-
  prt_table %>%
  # === Wide to Long: melt()
  melt(id.vars = c("field_size", "field_col", "model")) %>%
  # === Long to Wide: dcast()
  dcast(field_size + field_col + variable ~ model, value.var = "value") %>%
  .[variable == "yield", variable := "Yield"] %>%
  .[variable == "profit", variable := "Profit"] %>%
  .[order(field_col), ] %>%
  .[, field_col := NULL] %>%
  setnames(c("field_size", "variable"), c("Field Size", "Measurement"))

flextable(count_table) %>%
  merge_v(j = 1) %>%
  hline(i = c(3, 6)) %>%
  autofit() %>%
  fix_border_issues() %>%
  align(j = c(1, 2), align = "center")
```
